\section{Functional Requirements of the Testbench}\label{sec:functionalRequirements}

	According to the specification of the \textit{SAE J2522} and according to parameters considered to be important, some requirements for the testbench were defined.

	\begin{enumerate}
		\item Measure a braking force up to 250kgf.\label{itm:func-req-1}
		\begin{comment}
		\item Apply a braking pressure of at least 300 kPa.\label{itm:func-req-2}
		\end{comment}
		\item Measure temperatures up to 600 $^{\circ}$C\label{itm:func-req-3}
		\item Measure temperatures with a minimal resolution of 7.5 $^{\circ}$C.\label{itm:func-req-4}
		\item Accelerate the rotor to a speed up to 600 RPMs.\label{itm:func-req-5}
		\item System most have a sampling period of 50ms.\label{itm:func-req-6}
		\item The system hardware most be able to operate under temperatures up to 40$^{\circ}$C.\label{itm:func-req-7}
		\item System must have two acquisition channels for temperature.\label{itm:func-req-8}
		\item System must have a channel for braking force acquisition.\label{itm:func-req-9}
		\begin{comment}
		\item System must have a channel for vibration acquisition.\label{itm:func-req-10}
		\end{comment}
		\item System must have two digital outputs to control relays.\label{itm:func-req-11}
		\item System must have a channel for acquiring frequency.\label{itm:func-req-12}
		\item The system must work with real time acquisition.\label{itm:func-req-13}
		\begin{comment}
		\item The system must be able to detect when the sensors from the acquisition channels are disconnected.\label{itm:func-req-14}
		\end{comment}
	\end{enumerate}

	Also some other optional requirements were created for making the system more versatile for future tests, thoose being:

	\begin{itemize}
		\item Having an additional braking force acquisition channel.
		\item Having an additional output digital channel.
		\item Having three digital input channels.
		\item Having two analog outputs.
		\item Having a vibration acquisition channel
		\item Having a built-in USB to UART transceiver to make the system more practical to use.
		\item System being easily reprogrammable.
	\end{itemize}

\begin{comment}
\section{Software Requirements}\label{sec:software-requirements}
	
	\begin{enumerate}
		\item System must have a sampling rate of 50 ms.\label{itm:soft-req-1}
		\item System must be able to monitor six analog channels at once.\label{itm:soft-req-2}
		\item System must be able to control the digital outputs and one analog output during acquisition without loosing the real time constrain.\label{itm:soft-req-3}
		\item The data acquired does not need to be shown to user in real time.\label{itm:soft-req-4}
		\item The software layer must be able to record the data of the test.\label{itm:soft-req-5}
		\item The software highest layer must have a friendly GUI, advanced electronic and simple programmable knowledge cannot be a requirement to operate the software.\label{itm:soft-req-6}
		\item Calibration of the sensors data must be easy to modify on the software.\label{itm:soft-req-7}
		\item Software must be multiplatform.\label{itm:soft-req-8}
	\end{enumerate}
\end{comment}